Thesis Title

### 2022-04-11 chapters/introduction.tex
update thesis outline
Add aims of the thesis

@@

>>>>

\renewcommand*{\thefootnote}{\arabic{footnote}}

@@

\section{Aims of the Thesis}

Shotgun metagenomic approaches, defined by the sequencing of random  DNA fragments of microbial organisms directly from the biological sample, is a promising methodology to obtain very fast results for the identification of pathogens and their virulence and resistance properties directly from samples, without the need for culture. 
Standardisation of the method and validation of the statistical metrics used to analyse and report the data are of major importance to get this approach to be accredited and used in clinical settings.

The main objective of this work is to evaluate the use of bioinformatics methods for the analysis of metagenomic data to allow the rapid identification, virulence analysis and antimicrobial susceptibility prediction of pathogens with clinical relevance. The main goals are:

\begin{itemize}
    \item Evaluate the current impact and applicability of metagenomics genomics in medical microbiology, both in a clinical and in surveillance and infection prevention settings; 
    \item Develop novel methods and metrics to accurately identify and estimate relative abundance of pathogens of interest through a hybrid approach of read mapping and de novo assembly methods;
    \item Standardise the process of metagenomic analysis, allowing the comparison of results obtained across domains and stakeholders
    \item Develop computational efficient and robust frameworks that allows scientists and/or medical experts with limited programming experience to rapidly and easily query the abundance of specific taxa and genes across the samples of interest, obtaining simple and intuitive reports. 
\end{itemize}

As proof-of-concept, greater focus was given to clinically relevant taxa, such as Dengue virus. All methodologies and tools developed were tested and validated on both real and simulated data.
